---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vancomycin.calculator

<!-- badges: start -->
<!-- badges: end -->

The goal of vancomycin.calculator is to facilitate the dosing adjustments that are typically conducted in a hospital setting, and to allow clinical pharmacists to make patient specific judgements quicker. The function calculates a new dosing regimen for patients receiving Vancomycin using the Sawchuk-Zaske calculation strategy.

## Installation

You can install the development version of vancomycin.calculator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-akashp21/vancomycin.calculator")
```

## Examples
This is a basic example which shows you how to solve a common problem:

```{r example}
library(vancomycin.calculator)
## basic example code
Vanco_SS_dose_calculator(6.4, 24.3, 400, 8, 1, 2, 0, 37.5, 12.5) # should equal "This function recommends a new dose of 500 mg given over Q 8 h. This will produce a peak of 30.375 mg/L and a trough value of 8 mg/L"
Vanco_SS_dose_calculator(11.0, 22.1, 1000, 12, 1.5, 1.33333, 55/60, 35, 17.5) # should be "This function recommends a new dose of 1500 mg given over Q 12 h. This will produce a peak of 33.15 mg/L and a trough value of 15.2692370301831 mg/L"

```



