---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vancomycin.calculator

<!-- badges: start -->
<!-- badges: end -->

The goal of vancomycin.calculator is to facilitate the dosing adjustments that are typically conducted in a hospital setting, and to allow clinical pharmacists to make patient specific judgements quicker. The function calculates a new dosing regimen for patients receiving Vancomycin using the Sawchuk-Zaske calculation strategy.

## Installation

You can install the development version of vancomycin.calculator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-akashp21/vancomycin.calculator")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(vancomycin.calculator)
## basic example code
```

